CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-21 paper.Rmd
Remove library(devtools)
Update comments.

```{r, eval=FALSE}
library(devtools)
# (0) Use the CLPFUDatabase metapackage to install all dependencies.
#     This package installation step is needed only once.
devtools::install_github("EnergyEconomyDecoupling/CLPFUDatabase")

>>>>

```{r, eval=FALSE}
# (0) Use the CLPFUDatabase metapackage to install all dependencies.
#     This metapackage installation step is needed only once.
devtools::install_github("EnergyEconomyDecoupling/CLPFUDatabase")
